Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-12 manuscript/manuscript.tex

Additional technical challenges for large systems include high demands on memory and computation time;
we explain how to deal with those in the tutorials.

>>>>

Additional technical challenges for large systems include high demands on memory and computation time;
we explain how to deal with those in the tutorials (Notebook 00 and 02).
